Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
minor stuff

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train} (through a
\texttt{FeatureUninon}), selecting the best of those features and then feeding
them to a logistic regression model:
\begin{verbatim}
Pipeline([("pca", FeatureUnion([('linear_pca', PCA()),
                                ('kernel_pca', KernelPCA())])),
          ("feature_selection", SelectKBest()),
          ("logistic_model", LogisticRegression())
]).fit(X_train, y_train).predict(X_test)
\end{verbatim}

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUninon} can be
combined to create complex objects. In particular, since both are themselves
estimators, they can be used to form nested workflows. \textcolor{red}{TODO:
elaborate a bit more on nested constructions.}

>>>>

As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train} (through a
\texttt{FeatureUnion}), selecting the best of those features and then feeding
them to a logistic regression model:
\begin{verbatim}
Pipeline([("pca", FeatureUnion([('linear_pca', PCA()),
                                ('kernel_pca', KernelPCA())])),
          ("feature_selection", SelectKBest()),
          ("logistic_model", LogisticRegression())
]).fit(X_train, y_train).predict(X_test)
\end{verbatim}

As the above snippet shows, \texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex objects. In particular, since both are themselves
estimators, they can be used to form nested workflows. \textcolor{red}{TODO:
elaborate a bit more on nested constructions.}
